Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-10 journal/content.tex
Layout updates for thesis style
Moved validity and limitations to the end, organized conclusion chapter

\begin{table}
    \centering
    \begin{tabular}{ l l l }
        \toprule
        Database         & URL                         & N of matches   \\
        \midrule
        IEEExplore       & http://ieeexplore.ieee.org      & 745 \\ 
        ACM              & http://dl.acm.org               & 168 \\
        Scopus           & http://www.scopus.com/home.url  & 1596 \\
        Web of Knowledge & http://apps.webofknowledge.com  & 786 \\
        \bottomrule
    \end{tabular}
    \caption{Databases included in search, and number of matched articles}
    \label{table:databases}
\end{table}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/research_process_full.pdf}
    \caption{The study selection process}
    \label{fig:selectionprocess_full}
  \end{center}
\end{figure}

@@

\chapter{Discussion}
\label{sec:discussion}

@@

% ---------------------------------------------------------------------
\chapter{Limitations and future research}
\label{sec:conclusion}

* Compare to change leadership research, and organizational research. Which
  challenges are typical to any organization, which are specific to software
  development organizations.

* Compare how recommendations in large-scale application models of agile relate
  to the challenges and success factors reported in the transformation process.

>>>>

\begin{table}[b]
    \centering
    \begin{tabular}{ l l l }
        \toprule
        Database         & URL                         & N of matches   \\
        \midrule
        IEEExplore       & http://ieeexplore.ieee.org      & 745 \\ 
        ACM              & http://dl.acm.org               & 168 \\
        Scopus           & http://www.scopus.com/home.url  & 1596 \\
        Web of Knowledge & http://apps.webofknowledge.com  & 786 \\
        \bottomrule
    \end{tabular}
    \caption{Databases included in search, and number of matched articles}
    \label{table:databases}
\end{table}

@@

\begin{figure}[b]
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/research_process_full.pdf}
    \caption{The study selection process}
    \label{fig:selectionprocess_full}
  \end{center}
\end{figure}

@@

\chapter{Discussion and conclusions}
\label{sec:discussion}

In this chapter we discuss the results and provide a conclusion on this work.
First the results are discussed, including highlighting of most important
findings and comparison to previous work. Then we present limitations and
thereats to the validity of this work. This chapter ends with a concluding
overview of the work.

\section{Discussion}

* ...

@@

\section{Conclusion}

A concluding overview.

* Recap of the work

* Recap of mosti important results

(* Future research?)

% ---------------------------------------------------------------------
% \chapter{Limitations and future research}
% \label{sec:conclusion}
% 
% * Compare to change leadership research, and organizational research. Which
%   challenges are typical to any organization, which are specific to software
%   development organizations.
% 
% * Compare how recommendations in large-scale application models of agile relate
%   to the challenges and success factors reported in the transformation process.
